
##Read in the data

```{r}
dt <- read.csv('activity.csv')
dt$date <- as.POSIXct(dt$date)
```

##Plot a histogram of the data using ggplot2

```{r}
library(ggplot2)
library(lubridate)
library(dplyr)
dt_days <- group_by(dt, day(date))
dt_by_day <- summarise(dt_days, steps = sum(steps, na.rm = TRUE))
qplot(dt_by_day$steps, main = 'Histogram to show steps per day', xlab = "steps")
```

##Calculate mean and median
```{r}
meandt <- mean(dt_by_day$steps, na.rm =  TRUE)
mediandt <- median(dt_by_day$steps, na.rm =  TRUE)
```

The mean is `r meandt` and the median is `r mediandt`.

##Plot the average number of steps per day

```{r}

dt_int <- group_by(dt, interval)
dt_means <- summarise(dt_int, m = mean(steps, na.rm = TRUE))
qplot(data = dt_means, x = interval, y = m, geom = 'line')
max_steps <- max(dt_means$m)
max_int <- dt_means[dt_means$m == max_steps,1]
```

The inteval with the highest average step count across all days is `r max_int`.

##Inputting missing values

```{r}
missing_rows <- sum(!complete.cases(dt))
```

The number of incomplete cases is `r missing_rows`

Use the interval mean if the recorded value is NA.

```{r}
dt_narm <- merge(x = dt, y = dt_means, by = "interval", all.x = TRUE)
dt_narm[is.na(dt_narm$steps),"steps"] <- dt_narm[is.na(dt_narm$steps),"m"]

dt_narm_days <- group_by(dt_narm, day(date))
dt_narm_by_day <- summarise(dt_narm_days, steps = sum(steps, na.rm = TRUE))

```

Plotting a histogram

```{r}
qplot(dt_narm_by_day$steps, main = 'Histogram to show steps per day', xlab = "steps")
```

##Calculate mean and median
```{r}
meandt_narm <- mean(dt_narm_by_day$steps, na.rm =  TRUE)
mediandt_narm <- median(dt_narm_by_day$steps, na.rm =  TRUE)
```

The mean is `r meandt_narm` and the median is `r mediandt_narm`.

##Are there differences in activity patterns between weekdays and weekends?

```{r}
dt$weekday <- as.factor(ifelse(weekdays(dt$date) %in% c("Saturday","Sunday"), "Weekend", "Weekday"))

dt_by_wday  <- aggregate(x = dt$steps, 
                   by = list(dt$interval,dt$weekday), 
                   FUN = mean,
                   na.rm=TRUE)
names(dt_by_wday) <- c("interval","weekday","steps")
ggplot(dt_by_wday,
       aes(interval,steps)) +
       ggtitle("Time Series Plot of Average Steps by Interval") +
       facet_grid(. ~ weekday) +
       geom_line()

```
